\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application

### 2018-08-24 paper/paper.tex
remove one screenshot

The application has a taxi density heatmap (see figure \ref{fig:density}). The areas, which have many taxis at the given time, are colored red. Areas with less taxis are colored blue. The user interface has a time slider. When changing the time from \textit{15:00} to another time, the map would refresh. In the top left corner is a play button. With the play function, the map continually updates to the next time interval. Thus, the user can observe how the taxi density changes over time.

@@

The heatmap can visualize two different things. One of these is the number of picked up passengers. The other one is the number of dropped passengers. Figure \ref{fig:pickup} shows a screenshot with the pickup points heatmap. The user interface has a dropdown menu to let the user select which heatmap is displayed.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{img/pickup.png}
\caption{Pickup points heatmap}
\label{fig:pickup}
\end{figure}

>>>>

The application has a taxi density heatmap (see figure \ref{fig:density}). The areas, which have many taxis at the given time, are colored red. Areas with less taxis are colored blue. The user interface has a time slider. When changing the time from 3:00 PM to another time, the map would refresh. In the top left corner is a play button. With the play function, the map continually updates to the next time interval. Thus, the user can observe how the taxi density changes over time.

@@

The heatmap can visualize two other things. One of these is the number of picked up passengers. The other one is the number of dropped passengers. The user interface has a dropdown menu to let the user select which heatmap is displayed.
